---
title: "AssignmentB1"
author: "Apsara"
date: "2023-10-26"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(palmerpenguins)
library(tidyverse)
library(gapminder)
library(dplyr)
library(datateachr)
library(testthat)
```

```{r}
#Example of code I repeated a lot in my analysis

trees_average_diameter <- vancouver_trees %>%
  group_by(genus_name)%>%
  summarize(average_diameter= mean(diameter))
# Now we can look at this summarized data

view(trees_average_diameter)
```
Now, I will make a function that takes in a dataset and groups by a certain categorical variable. I will also make it such that function finds the mean of another numeric variable of the grouped variable.

```{r}
#' @title Documentation for average_by_group function
#' @description This function is meant to help summarize the dataset, by essentially taking in a categorical variable that the user wants to group the data by, and then calculating the mean of a specific numeric variable that the user inputs. 
#' @param data character (1) string, This is the input dataset that the user is working with. I named this argument because it is where the user inputs the dataset they are working with.
#' @param group character (1) string, This is the categorical variable that the user wants to group the dataset by. I names this as group because it specifies the group or categorical variable the user wants to categorize the data by.
#' @param numeric_category character (1) string, This is the numeric variable that the user wants to find the mean of, grouped by the 'group' variable. I names this numeric_category because it lets the user know that this is the numerical category that the mean will be calculated from. 
#' @param na.rm logical value, This is how NA values will be handled in the data. By default, it is set to FALSE, but the user can change the input 
#' @param ... This allows the user to specify any additional inputs to be used within the mean function
#'
#' @return tibble, returns a tibble with the data summarized by group and by the average of a numeric variable within the groups.

average_by_group <- function(data, group, numeric_category, na.rm= FALSE, ...) 
  # Check if group is numeric and numeric_category is not
  {check_numerical <- data %>%
    pull({{numeric_category}}) %>%
    is.numeric
  
if (check_numerical) {data %>%
    group_by({{group}})%>%
    summarize(average_variable = mean({{numeric_category}}, na.rm= na.rm, ...))
  }
else stop("The group variable must not be numeric.")
  }
```
Examples
Example 1: Check if the function works
```{r}
#I will demonstrate the use of this function from the vancouver trees dataset
vancouver_trees
average_by_group(vancouver_trees, genus_name, diameter)
```
Example 2: A different dataset
```{r}
#For my second example, I will use the penguins dataset, so show the generality of my function
average_by_group(penguins, island, bill_length_mm)

# Note that here the NAs show up because i set the default value to FALSE< so the NAs are not excluded.
#But I could also change the setting so that NAs are set to true, and I can pass additional values. Here, I will try to find the average bill_length for species that have no NA values, and I set the trim value to 0.1.

average_by_group(penguins, species, bill_length_mm, na.rm = TRUE, trim=0.1)

```
Example 3: To show an error incase the user inputs a numerical categorical variable that is not actually numeric
```{r, error=TRUE}
average_by_group(penguins, species, island)
```
Testing the function
```{r}
#Lets test that inputing a non numeric variable gives me an error
expect_error(average_by_group(vancouver_trees, genus_name, std_street))

# Additional Tests
test_that("Tests for average_by_group function", {
  
  # Test 1: Vector with no NAs
  df1 <- tibble(group = c("A", "A", "B", "B"), value = c(10, 20, 30, 40))
  expect_equal(average_by_group(df1, group, value), tibble(group = c("A", "B"), average_variable = c(15, 35)))
  
  # Test 2: Vector that has NAs
  df2 <- tibble(group = c("A", "A", "B", "B"), value = c(10, NA, 30, 40))
  expect_no_error(average_by_group(df2, group, value))

  # Test 3: Vector of a different type (using a character vector for numeric_category which should cause an error)
  df3 <- tibble(group = c(1, 2, 3, 4), value = c("A", "B", "C", "D"))
  expect_error(average_by_group(df3, group, value))
  
  # Test 4: Vector of length 0
  df4 <- tibble(group = character(0), value = numeric(0))
  expect_equal(average_by_group(df4, group, value), tibble(group = character(0), average_variable = numeric(0)))

})
```



